SDR enhancement by clouds

### 2024-02-26 article/article.Rmd
Commit 2024-02-26 15:09

```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
suppressMessages({
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
})
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

>>>>

```{r setup, echo=F, include=FALSE}
rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                               strip.white = TRUE,
                               sep = ";",
                               header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```
